---
title: "Breast Cancer Identification"
author: "Dimensionless"
date: "October 29, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
### Objective 
In an almost universal paradigm, the CAD problem is addressed by a 4 stage system:

1)Candidate generation which identifies suspicious unhealthy candidate regions of interest (candidate ROIs, or simply candidates) from a medical image;
2) Feature extraction which computes descriptive features for each candidate so that each candidate is represented by a vector x of numerical values or attributes;
classification which differentiates candidates that are malignant cancers from the rest of the candidates based on x; and
visual presentation of CAD findings to the radiologist.
In this challenge, we focus on stage 3, learning the classifier to differentiate malignant cancers from other candidates.
### Importing the data from "Breast Cancer Info"
```{r Importing}
info<-read.table("Breast Cancer Info.tsv",header = F,sep = "\t")
info$V12<-NULL
col_names<-c("label","image-finding-id","study-finding-id","image-id","patient-id","leftbreast","MLO","x-location","y-location","x-nipple-location","y-nipple-location")
colnames(info)<-col_names
# Importing features file
features<-read.delim("Features.txt",header = F)
features$V118<-NULL
```
### Exploring the data
```{r Exploration}
str(info)
table(info$label)
table(info$`image-finding-id`)
table((subset(info,info$`patient-id`==14280))$`image-id`)
library(dplyr)
info%>%filter(`patient-id`==14280 )%>%select(`study-finding-id`)
length(unique(info$`patient-id`))
unique(info$`study-finding-id`)
```
### Combining the data
```{r}
dataset<-cbind(info,features)
class(dataset)
```
### Splitting the data
```{r Splitting}
library(caTools)
set.seed(1)
split<-sample.split(dataset$label,SplitRatio = 0.5)
table(split)
train<-dataset[split,]
table(train$label)
length(unique(train$`patient-id`))
test<-dataset[!split,]
length(unique(test$`patient-id`))
